### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:19	00:32:47	(Wed19.Mar)
la2pdf commit - 2014:03:19	00:40:40	(Wed19.Mar)

\ai{TODO}

>>>>

\ai{The explanation is provided in the section V, the discussion. We have now rewritten the relevant paragraphs to include answers to these and other comments. Regarding the discussion of the FLOPS these were never intended to be an accurate representation of the run-times but rather to provide an indication of how efficiently we are able to harness the GPU's resources.}
